### 2025-09-05 submissions/03-jpam-RR/manuscript_main.tex
edits to mansuscript to address some of R1's comments. I also added probit and logit models for comparison with the lpm results.

@@

The rest of this paper proceeds as follows. First, I discuss the theoretical framework in section (\ref{sec:model}). Second, I describe the data sources in section (\ref{sec:data}). Third, I present the empirical approach and results in sections (\ref{sec:empstrat}) and (\ref{sec:results}). Fourth, I discuss robustness checks and alternative explanations in section (\ref{sec:robcheck}). Finally, I conclude in section (\ref{sec:conc}).

@@

The objective ancestry measure—distinct from subjective racial identification where respondents select ``Asian'' as their race—depends on birthplaces across three generations. The three identifiable generations include: 1) first-generation immigrants born in Asian countries with both parents also born in Asian countries, 2) second-generation individuals who are US-born citizens with at least one parent born in an Asian country, 3) third-generation Asian Americans who are US-born citizens with two US-born parents and at least one grandparent born in an Asian country.\footnote{I restrict first-generation cases to those whose parents were born in Asian countries to exclude US citizens born abroad to American parents.} The sample includes Asian Americans, first-, second-, and third-generation immigrants aged 17 and younger living with parents between 2004 and 2021. Summary statistics appear in Table (\ref{tab:sumstat1}).

@@

I develop another racial animus proxy using ANES surveys \autocite{anes2021} measuring discrimination against Black Americans. ANES, conducted since 1948, enjoys widespread political science usage. The survey examines attitudes toward different racial groups, voting intentions, and political questions. I employ several 2004-2020 ANES questions measuring racial animus. The racial animus index averages responses across multiple animus-measuring questions.\footnote{Questions parallel those used by \textcite{charlesPrejudiceWagesEmpirical2008}: (1) ``Conditions Make it Difficult for Blacks to Succeed'', (2) ``Blacks Should Not Have Special Favors to Succeed'', (3) ``Blacks Must Try Harder to Succeed'', (4) ``Blacks Gotten Less than They Deserve Over the Past Few Years'', and (5) ``Feeling Thermometer Toward Asians.''}

@@

The research opens several avenues for future investigation. First, scholars could examine how recent anti-Asian violence following COVID-19 has influenced identity patterns, providing natural experiments in bias effects. Second, researchers might explore identity choices in specific institutional contexts like college admissions or workplace advancement, where model minority stereotypes create complex incentive structures. Third, analysis could extend to other Asian American subgroups, recognizing that Chinese, Korean, Vietnamese, and other communities face distinct stereotypes and discrimination patterns.

>>>>

While my formal theoretical model provides a logical framework for understanding how bias affects racial identity, the behavioral literature on racial identity and assimilation offers crucial empirical insights that complement this theoretical approach. Research in this tradition emphasizes how racial identity is not merely a cognitive construct but is actively performed, negotiated, and reconstructed through daily interactions and life experiences \autocite{waters1990ethnic}. \textcite{telles2008generations} study of Mexican Americans demonstrates how individuals strategically adapting their racial presentations across different social contexts while maintaining core identity elements across generations. Similarly, behavioral studies have documented how discrimination experiences shape identity salience and group attachment, with individuals developing adaptive strategies that range from ethnic distancing to reactive ethnicity depending on situational factors \autocite{zhou1997segmented}. This behavioral perspective reveals that racial identity operates as both a response to external categorization and an active process of boundary maintenance \autocite{cornell2006ethnicity}. While this literature has primarily relied on qualitative observations and ethnographic methods to document identity flexibility, the present analysis advances this understanding by quantifying these strategic choices through systematic comparison of objective ancestry measures with subjective racial identification across varying environmental contexts.

@@

@@

The objective ancestry measure—distinct from subjective racial identification where respondents select ``Asian'' as their race—depends on birthplaces across three generations. The three identifiable generations include: 1) first-generation immigrants born in Asian countries with both parents also born in Asian countries, 2) second-generation individuals who are US-born citizens with at least one parent born in an Asian country, 3) third-generation Asian Americans who are US-born citizens with two US-born parents and at least one grandparent born in an Asian country. It is important to note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may not be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents. The sample includes Asian Americans, first-, second-, and third-generation immigrants aged 17 and younger living with parents between 2004 and 2021. Summary statistics appear in Table (\ref{tab:sumstat1}).

@@

I develop another racial animus proxy using ANES surveys \autocite{anes2021} measuring discrimination against racial groups. ANES, conducted since 1948, enjoys widespread political science usage. The survey examines attitudes toward different racial groups, voting intentions, and political questions. I employ several 2004-2020 ANES questions measuring racial animus. The racial animus index averages responses across multiple animus-measuring questions.\footnote{Questions parallel those used by \textcite{charlesPrejudiceWagesEmpirical2008}: (1) ``Conditions Make it Difficult for Blacks to Succeed'', (2) ``Blacks Should Not Have Special Favors to Succeed'', (3) ``Blacks Must Try Harder to Succeed'', (4) ``Blacks Gotten Less than They Deserve Over the Past Few Years'', and (5) ``Feeling Thermometer Toward Asians.''} While the ANES racial animus questions primarily focus on attitudes toward Black Americans, research demonstrates that racial prejudices are highly correlated across different minority groups, with individuals who express bias toward one racial minority typically holding similar attitudes toward others \autocite{almasalkhi2023links, mora2020antiblackness}. These measures therefore capture broader patterns of racial animus that extend beyond anti-Black sentiment specifically. When combined with the Asian-focused IAT measures and hate crimes against Asian Americans in my composite index, this multi-proxy approach weights the bias measure more heavily toward Asian-specific prejudice while still capturing the general racial climate.

@@

The research opens several avenues for future investigation. First, scholars could examine how recent anti-Asian violence following COVID-19 has influenced identity patterns, providing natural experiments in bias effects. Second, researchers might explore identity choices in specific institutional contexts like college admissions or workplace advancement, where model minority stereotypes create complex incentive structures. Third, analysis could extend to other Asian American subgroups, recognizing that Chinese, Korean, Vietnamese, and other communities face distinct stereotypes and discrimination patterns. Fourth, more granular geographic units, such as counties, city, or zip-code level, could provide a more precise measure of local bias. However, data limitations prevent the use of these finer geographic levels in the current analysis. Future research could explore this question using more detailed geographic identifiers if such data becomes available, allowing for a deeper understanding of how local contexts shape racial identity.

### 2025-09-05 submissions/03-jpam-RR/submit_journal.tex
edits to mansuscript to address some of R1's comments. I also added probit and logit models for comparison with the lpm results.

    \section{Responses to Referee One}
    \begin{spacing}{\rrquote}
    \begin{quotation}
    \textbf{R1: } 1. 
    \end{quotation}
    \end{spacing}

    \section{Responses to Referee Two}
    \begin{spacing}{\rrquote}
    \begin{quotation}
    \textbf{R2: } 1. 
    \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
    \end{spacing}

    \clearpage
    \pagebreak
    \end{refsection}

>>>>

    \section{Responses to Referee One}
        I would like to thank referee one for the insightful comments and suggestions. Below is a detailed response to the comments and suggestions.
    \begin{spacing}{\rrquote}
    \begin{quotation}
    \textbf{R1: } 1. Beginning with the paper's theoretical account of racial bias and its potential impact on racial identity, I appreciate the author's use of formal theory to present a logical and rational model explaining why bias may affect racial identity. However, I feel the author misses an important literature on racial identity and assimilation that focuses on the behavioral aspects of race and racial identity. While they do briefly touch on some of this literature, I suggest that revisions have a greater focus on the behavioral literature on racial identity and assimilation in addition to the formal model. A good work that I could suggest on this topic is Telles and Ortiz's Generations of Exclusion.
    \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I thank the referee for this suggestion. I have added a paragraph in the introduction discussing Telles and Ortiz's Generations of Exclusion and other related works on racial identity and assimilation. Specifically, I add the following paragraph in the introduction: ``While my formal theoretical model provides a logical framework for understanding how bias affects racial identity, the behavioral literature on racial identity and assimilation offers crucial empirical insights that complement this theoretical approach. Research in this tradition emphasizes how racial identity is not merely a cognitive construct but is actively performed, negotiated, and reconstructed through daily interactions and life experiences \autocite{waters1990ethnic}. \textcite{telles2008generations} study of Mexican Americans demonstrates how individuals strategically adapting their racial presentations across different social contexts while maintaining core identity elements across generations. Similarly, behavioral studies have documented how discrimination experiences shape identity salience and group attachment, with individuals developing adaptive strategies that range from ethnic distancing to reactive ethnicity depending on situational factors \autocite{zhou1997segmented}. This behavioral perspective reveals that racial identity operates as both a response to external categorization and an active process of boundary maintenance \autocite{cornell2006ethnicity}. While this literature has primarily relied on qualitative observations and ethnographic methods to document identity flexibility, the present analysis advances this understanding by quantifying these strategic choices through systematic comparison of objective ancestry measures with subjective racial identification across varying environmental contexts.''
    \end{spacing}

    \begin{spacing}{\rrxspc}
    \begin{quotation}
        \textbf{R1: } 2. As for the methods, I have a few concerns that I hope the author can address in future drafts. One concern that looms over the paper for me is that the 'objective' measure of Asian background may not be as objective as it seems. For instance, it is unclear that, say, the children or grandchildren of people who were born to non-asian parents in Asia, for example, on an American military base, would be classified as Asian. I don't think this is a huge concern for the analysis, but it needs to at least be addressed.
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrxspc}
        \textbf{Response:} I appreciate the referee's attention to this issue. It is a point I address in the paper's data section in the following footnote ``I restrict first-generation cases to those whose parents were born in Asian countries to exclude US citizens born abroad to American parents''. Following the comment, I am going to add a few sentences to clarify this point. Specifically, I will add the following sentences in the data section: ``It is important to note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may not be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents.''
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 3. Second, I am concerned that using the state as the unit of analysis for regional bias may be problematic. Perhaps the bias of the community that one grows up in would be better measured at the city or zip-code level. For instance, those who live in Austin, Texas may have a very different experience with bias than those who live in rural west Texas. If the authors could provide even a supplemental analysis in which they analyze this at local level, this would help significantly to alleviate these concerns.
    \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrxspc}
            \textbf{Response:} I thank the referee for this suggestion. I agree that using more granular geographic units would provide a more precise measure of local bias. However, there are major data limitations that prevent me from doing so. First, the CPS does not provide geographic identifiers below the county level and only for 45\% of the sample and only for counties with larger populations. Therefore, if used at the county level, I would lose more than half of the sample and potentially introduce bias. Second, even if I had access to more granular geographic identifiers in the CPS, to my knowledge, there are no measures of racial bias at more granular geographic levels. The General Social Survey (GSS), which I use as one of my measures of racial bias, is only representative at the the state level. The American National Election Studies (ANES) is only available at the state level. The Uniform Crime Reports (UCR), which I use to calculate anti-Asian hate crimes, is recommended to not be used at the county level and is not available at lower levels. The Implicit Association Test (IAT) data is the only dataset that available at the county level, however, many social scientists have raised concerns about using the IAT on it's own. Therefore, while I agree with the referee that using more granular geographic units would be ideal, I am limited by data availability. I will add a paragraph to the conclusion discussing this limitation and suggesting that future research could explore this question using more granular geographic units if data becomes available. Specifically, I will add the following paragraph to the conclusion: ``More granular geographic units, such as counties, city, or zip-code level, could provide a more precise measure of local bias. However, data limitations prevent the use of these finer geographic levels in the current analysis. Future research could explore this question using more detailed geographic identifiers if such data becomes available, allowing for a deeper understanding of how local contexts shape racial identity.''
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 4. Additionally, while I understand why children are of particular interest, I would also like to see what the results look like for Asian adults. Is this phenomenon of calculating one's identity concentrated among children? Do they come to identify more with their Asian roots as they reach adolescence and adulthood? Are the same calculations being made by adults? These are important questions that including the sample of adults could be useful to help answer.
        \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 5. Lastly and importantly, it is also unclear to me why the author uses measures of animus towards African Americans from the ANES in their bias index, especially when measures of animus towards Asian Americans are available on the very same study. Here I think the author either needs to make a case for the bias they are interested in being more broad than just bias toward Asian-Americans or they need to reestimate their measures of bias.
        \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
       Thank you for this important methodological observation. You raise a valid point about the conceptual alignment between my bias measures and outcomes. Let me clarify my approach: The ANES racial animus questions do primarily focus on attitudes toward Black Americans, I also use measures of animus toward Asian Americans. Research consistently shows that racial prejudices are highly correlated across different minority groups—individuals who express bias toward one racial minority typically hold similar attitudes toward others \autocite{almasalkhi2023links, mora2020antiblackness}. These measures therefore capture general patterns of racial animus rather than group-specific bias alone. Crucially, my composite bias index combines three distinct components: (1) Asian-focused IAT measures, (2) ANES racial animus questions, and (3) hate crimes specifically targeting Asian Americans. This multi-proxy approach effectively weights the overall bias measure toward Asian-specific prejudice (two of three components directly measure anti-Asian sentiment) while incorporating information about the broader racial climate through the ANES measures. This methodological choice serves two purposes: it reduces measurement error through the composite approach while capturing both specific anti-Asian bias and the general environment of racial prejudice that affects all minority groups. 
    \end{spacing}
    \clearpage
    \pagebreak

    \section{Responses to Referee Two}
    I would like to thank referee two for the insightful and constructive comments and suggestions. Below is a detailed response to the comments and suggestions.

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 1. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 2. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 3. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 4. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 5. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

    \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 6. 
        \end{quotation}
        \end{spacing}

        \begin{spacing}{\rrxspc}

    \end{spacing}

    \end{refsection}

\clearpage
\pagebreak
